Influence of Connectivity on Dung Beetle Communities

### 2025-02-26 corridor_docs/eric_ms_thesis/thesis_planning.Rmd
added table and fig

>>>>

btl_sums_patch<-btl_data %>%
  select(-sum) %>% 
  pivot_longer(pvin:ostr,names_to = "species",values_to = "n") %>% 
  group_by(patch) %>%
  summarize(n=sum(n, na.rm=TRUE)) %>%
  arrange(patch,desc(n)) %>% 
  mutate(patch=case_when(
    patch == "c" ~ "Corridor",
    patch == "m" ~ "Matrix",
    patch == "w" ~ "Winged",
    patch == "r" ~ "Rectangle",
    .default = as.character(patch)))

abund_patch<-knitr::kable(btl_sums_patch, 
      digits = 2,
      align="lr",
      format="latex",
      row.names = FALSE,
      booktabs=T,
      linesep = "", #removes the blank line after every 5 lines
      caption = "Total dung beetles captured in all replicates of a patch type.") %>%
  kable_styling(bootstrap_options = c("striped"),
                full_width = F,
                latex_options="scale_down",
                font_size = 12,
                position = "left") %>% 
  # column_spec(1, italic = T) %>% 
  row_spec(0, bold = T) 
  # row_spec(1:15, hline_after = T) 
abund_patch
